A High-Order Discontinuous Galerkin Solver with Dynamic Adaptive Mesh Refinement to Simulate Cloud Formation Processes

### 2019-10-23 writing/paper/paper.tex
State more clearly that Taylor-Green/ABC are not an exact solution.
Add draft for manufactured solution.

\section{Results}
We use a mix of various benchmarking scenarios that consist of standard \textsc{cfd} scenarios and atmospheric flows.
%
For the standard \textsc{cfd} testing scenarios, we use the following constants of fluids:
\begin{equation}
  \gamma = 1.4, \quad \Pr = 0.7, \quad c_v = 1.0.
\end{equation}
A simple scenario is the Taylor-Green vortex.
It has an analytical solution in the incompressible limit which is given by
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) \cos(y) \\
- \cos(x) \sin(y) 
    \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C.
  \end{split}
\end{align}
The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number $\text{Ma} = 0.1$~\cite{dumbser2016high}. The viscosity is set to $\mu = 0.1$.

We simulate on the domain $[0,2\pi]^2$ 
%We use a domain of size 
%$(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ 
%% keine Meter-Angaben bei analytischen Testcases
and impose the analytical solution at the boundary.
A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (\cref{fig:taylor-green}) shows excellent agreement.
We used an \aderdg{}-scheme of order $5$ with a grid of $25^2$ cells.

@@

The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but possesses an analytical solution for three-dimensions as well~\cite{tavelli2016staggered}.
It is defined in the domain \( \left[ -\pi, \pi \right]^3 \) as
\begin{align}
  \label{eq:abc-flow}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \phantom{-} \exp(-1\mu t)
  \begin{pmatrix}
    \sin(z) + \cos(y)\\
    \sin(x) + \cos(z)\\
    \sin(y) + \cos(x)
  \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
  + C.
  \end{split}
\end{align}
again under the assumption of incompressibility.
The constant $C = \nicefrac{100}{\gamma}$ is chosen as before.
We use a viscosity of $\mu = 0.01$ and analytical boundary conditions.
Our results (\cref{fig:abc-flow}) show a good agreement between the analytical solution and our approximation with an \aderdg{}-scheme of order $3$ with a mesh consisting of $27^3$ cells at time $t = \SI{0.1}{\s}$.

>>>>

\section{Results}
\todo{Introduction of chapter}
\todo{Introduce need for MMS}
Following~\cite{dumbser2010arbitrary}, we assume that
\begin{align}\label{eq:manufactured-solution}
\begin{split}
  \pressure(\bm{x}, t) &= \pressure_0 \cos( \bm{k} \bm{x} - \omega t ) + \pressure_b, \\
  \Qrho(\bm{x}, t) &= \Qrho_0 \sin (\bm{k} \bm{x} - \omega t) + \Qrho_b, \\
  \Qv(\bm{x}, t) &= \bm{v_0} \sin(\bm{k} \bm{x} - \omega t),
\end{split}
\end{align}
is our analytical solution.
We use the constants
\begin{equation}
\begin{alignedat}{6}
  & \pressure_u &&= \nicefrac{1}{10}, \qquad& \pressure_b &= \nicefrac{1}{\gamma}, \\
  & \Qrho_0 &&= \nicefrac{1}{2}, \qquad& \Qrho_b &= 1, \\
  & \bm{v_0} &&= \nicefrac{1}{4},
  \begin{pmatrix}
    1 \\
    1
  \end{pmatrix},
  \qquad& \bm{k} &= \nicefrac{\pi}{5}
  \begin{pmatrix}
    1\\
    1
  \end{pmatrix},\\
  & \omega &&= 2 \pi.
  \end{alignedat}
\end{equation}
\Cref{eq:manufactured-solution} does not solver the compressible Navier-Stokes equations \cref{eq:equation-set} directly but rather our equation set with ann added source term.
We derive this source term symbolically with a computer algebra system.

We use a mix of various benchmarking scenarios that consist of standard \textsc{cfd} scenarios and atmospheric flows.

For the standard \textsc{cfd} testing scenarios, we use the following constants of fluids:
\begin{equation}
  \gamma = 1.4, \quad \Pr = 0.7, \quad c_v = 1.0.
\end{equation}

A simple scenario is the Taylor-Green vortex.
It has an analytical solution in the incompressible limit which is given by
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) \cos(y) \\
- \cos(x) \sin(y) 
    \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C.
  \end{split}
\end{align}
The constant $C = \nicefrac{100}{\gamma}$ governs the speed of sound and thus the Mach number $\text{Ma} = 0.1$~\cite{dumbser2016high}. The viscosity is set to $\mu = 0.1$.

We simulate on the domain $[0,2\pi]^2$ 
%We use a domain of size 
%$(\SI{2 \pi}{\m} \times \SI{2 \pi}{\m})$ 
%% keine Meter-Angaben bei analytischen Testcases
and impose the analytical solution at the boundary.
A comparison at time $t = 10.0$ of the analytical solution for the pressure with our approximation (\cref{fig:taylor-green}) shows excellent agreement.
Note that we only show a qualitative analysis because this is not an exact solution for our equation set.
We used an \aderdg{}-scheme of order $5$ with a grid of $25^2$ cells.

@@

The Arnold-Beltrami-Childress (\textsc{abc}) flow is similar to the Taylor-Green vortex but possesses an analytical solution for three-dimensions as well~\cite{tavelli2016staggered}.
It is defined in the domain \( \left[ -\pi, \pi \right]^3 \) as
\begin{align}
  \label{eq:abc-flow}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \phantom{-} \exp(-1\mu t)
  \begin{pmatrix}
    \sin(z) + \cos(y)\\
    \sin(x) + \cos(z)\\
    \sin(y) + \cos(x)
  \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
  + C.
  \end{split}
\end{align}
again under the assumption of incompressibility, i.e.\ it is also not an exact solution of our \pde{}.
The constant $C = \nicefrac{100}{\gamma}$ is chosen as before.
We use a viscosity of $\mu = 0.01$ and analytical boundary conditions.
Our results (\cref{fig:abc-flow}) show a good agreement between the analytical solution and our approximation with an \aderdg{}-scheme of order $3$ with a mesh consisting of $27^3$ cells at time $t = \SI{0.1}{\s}$.
